Make any stupid plot you want

### 2021-02-26 draft/sections/math.tex
through retraction fig
render image, going w/ minor rework of old one

\begin{figure}[H]
    \includegraphics[width=.5\linewidth]{figures/math/fiberbundle.png}
    \caption{ Fiber (time, temperature) with an interval \dbase\ basespace. The sections $\dsection_i$ and $\dsection_j$ are constrained such that the time variable must be monotonic, which means each section is a timeseries of temperature values. They are included in the global set of sections  $\dsection_1, \dsection_2 \in \Gamma(\dtotal)$}
    \label{fig:data_sections}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=1\textwidth]{figures/math/retraction_maps.png}
    \caption{The scatter and line graphic base spaces have one more dimension of continuity than \dbase\ so that \gbase\ can encode physical aspects of the glyph, such as shape (a circle) or thickness. The image has the same dimension in \gbase\ as in \dbase. \note{add $\alpha, \beta$ coordinates to figures}}
    \label{fig:graphic_retraction_map}
\end{figure}

@@

\subsubsection{Renderering \gsection}
\label{sec:graphic_section}
\begin{figure}
    \includegraphics[width=\textwidth]{figures/math/graphic_render.png}
    \caption{To render a graphic, a pixel $p$ is selected in the display space, which is defined in the same coordinates as the x and y components in \gfiber\.  The inverse mapping ${\gsection_{xy}}^(p)$ returns a region $\gbase_{p} \subset \gbase$. $\gsection(\gbase_{p})$ returns the list of elements $(x,\,y,\,r,\,g,\,b) \in \gfiber$ that lie over $\gbase_{p}$. The integral over the $(r,\,g,\,b)$ elements is the color of the pixel.}
    \label{fig:graphic_rho_lookup}
\end{figure}

>>>>

\begin{figure}[H]
    \includegraphics[width=1\linewidth]{figures/math/fiberbundle.png}
    \caption{ Fiber (time, temperature) with an interval \dbase\ basespace. The sections $\dsection_i$ and $\dsection_j$ are constrained such that the time variable must be monotonic, which means each section is a timeseries of temperature values. They are included in the global set of sections  $\dsection_1, \dsection_2 \in \Gamma(\dtotal)$}
    \label{fig:data_sections}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=1\textwidth]{figures/math/retraction_maps.png}
    \caption{The scatter and line graphic base spaces have one more dimension of continuity than \dbase\ so that \gbase\ can encode physical aspects of the glyph, such as shape (a circle) or thickness. The image has the same dimension in \gbase\ as in \dbase.}
    \label{fig:graphic_retraction_map}
\end{figure}

@@

\subsubsection{Renderering \gsection}
\label{sec:graphic_section}
\begin{figure}
    \includegraphics[width=\textwidth]{figures/math/render.png}
    \caption{To render a graphic, a pixel $p$ is selected in the display space, which is defined in the same coordinates as the x and y components in \gfiber.  The inverse mapping ${\gsection_{xy}}^(p)$ returns a region $\gbase_{p} \subset \gbase$. $\gsection(\gbase_{p})$ returns the list of elements $(x,\,y,\,r,\,g,\,b) \in \gfiber$ that lie over $\gbase_{p}$. The integral over the $(r,\,g,\,b)$ elements is the color of the pixel.}
    \label{fig:graphic_rho_lookup}
\end{figure}
